Twists of supersymmetric gauge theories

### 2019-09-04 paper.tex
Minor edits to 4d section

The 4-dimensional $\mc N=1$ pure super Yang-Mills theory has BRST fields given by a ghost $c$, a 4d gauge field $A$, and a Lie algebra valued Weyl spinor field $\lambda$. 
In addition, $4$-dimensional supersymmetry supports a chiral (anti-chiral matter) multiplet, which comprises a complex scalar $\phi$ and a left (right) Weyl spinor $\psi_+$ ($\psi_-$).

The most general theory $4$-dimensional $\mc N = 1$ theory we will consider is super Yang-Mills theory valued in a Lie algebra $\fg$ coupled to a chiral multiplet with values in a complex $\fg$-representation $R$. 
This means that the fields $\phi, \psi_+$ take values in $R$ and $\Bar{\phi}, \psi_-$ take values in $R^*$. 
We have written down the action for supersymmetric Yang-Mills numerous times. 
The kinetic action for $4$-dimensional $\mc N = 1$ matter is of the form
\[
S_{\rm matter} (\phi, \Bar{\phi}, \psi_+, \psi_-) = \int \d^4 x \; \<\partial_{x_i} \phi , \partial_{x_i} \Bar{\phi}\>_R + \int \d^4 x \; \<\psi_+ , \sd \dd \psi_-\>_R .
\]
Here $\<-,-\>_R$ denotes the obvious pairing between $R$ and $R^*$. 
Super Yang-Mills couples to the matter via the action 
\[
S_{\rm couple} = \int \d^4 x \;
\]

The action by supersymmetry for the $4$-dimensional matter theory is encoded by a linear and quadratic functional
\begin{align*}
I^{(1)} (Q_+, Q_-) & = \int \<\phi^*, (Q_+, \psi_+)\>_R + \int \<\Bar{\phi}^*, (Q_-, \psi_-)\>_R + \int \<\psi^*_+, Q_+ \d \phi\>_R + \int \<\psi_-^*, Q_- \d \Bar{\phi}\>_R \\
I^{(2)} (Q_+ \otimes Q_-) & = \int \<\psi^*_- , \rho(\Gamma(Q_+, Q_-)) \psi_+\>_R
\end{align*}

There is a single non-zero equivalence class of square zero supercharges in $4$-dimensional $\mc N = 1$, which we fix from hereon. 
Such supercharges are minimal (i.e. have 2d image).  
They are stabilized by $\SU(2)$ \brian{really $U(2)$, i think}.  
The R-symmetry group is $U(1)$, and so the twisted theory by such a supercharge is always $\ZZ$-graded.

>>>>

The 4-dimensional $\mc N=1$ pure super Yang-Mills theory has BRST fields given by a ghost $c$, a 4d gauge field $A$, and a Lie algebra valued Weyl spinor field $\lambda$. 
In addition, $4$-dimensional supersymmetry supports a chiral (or anti-chiral) matter multiplet, which comprises a complex scalar $\phi$ and a left (right) Weyl spinor $\psi_+$ ($\psi_-$).

The most general theory $4$-dimensional $\mc N = 1$ theory we will consider is super Yang-Mills theory valued in a Lie algebra $\fg$ coupled to a chiral multiplet with values in a complex $\fg$-representation $R$. 
This means that the fields $\phi, \psi_+$ take values in $R$ and $\Bar{\phi}, \psi_-$ take values in $R^*$. 
We have written down the action for supersymmetric Yang-Mills theory numerous times. 
The kinetic part of the action functional for $4$-dimensional $\mc N = 1$ matter is of the form
\[
S_{\rm matter} (\phi, \Bar{\phi}, \psi_+, \psi_-) = \int \d^4 x \; \<\partial_{x_i} \phi , \partial_{x_i} \Bar{\phi}\>_R + \int \d^4 x \; \<\psi_+ , \sd \dd \psi_-\>_R .
\]
Here $\<-,-\>_R$ incorporates the obvious pairing between $R$ and $R^*$. 
Super Yang-Mills couples to the matter via the action 
\[
S_{\rm couple} = \int \d^4 x \;
\]

The action of supersymmetry on the $4$-dimensional matter theory is encoded by a linear and quadratic functional:
\begin{align*}
I^{(1)} (Q_+, Q_-) & = \int \<\phi^*, (Q_+, \psi_+)\>_R + \int \<\Bar{\phi}^*, (Q_-, \psi_-)\>_R + \int \<\psi^*_+, Q_+ \d \phi\>_R + \int \<\psi_-^*, Q_- \d \Bar{\phi}\>_R \\
I^{(2)} (Q_+ \otimes Q_-) & = \int \<\psi^*_- , \rho(\Gamma(Q_+, Q_-)) \psi_+\>_R.
\end{align*}

There is a single non-zero equivalence class of square zero supercharges in $4$-dimensional $\mc N = 1$, which we fix from here on. 
Such supercharges are minimal (i.e. have 2d image).  
They are stabilized by $\SU(2)$ \brian{really $U(2)$, i think} \chris{Agreed: a minimal square zero spinor of positive helicity is stabilized by $\SU(2)_-$, but also by a torus in $\SU(2)_+$.}.  
The R-symmetry group is $U(1)$, and the twisted theory by such a supercharge can always be made $\ZZ$-graded.
